Supporting information

### 2019-08-23 EAshiklomanovSA2.Rmd
Add more detailed prior information

```{r libraries, include = FALSE}
library(knitr)
library(kableExtra)
library(drake)
library(ggplot2)
library(GGally)

@@

>>>>

```{r libraries, include = FALSE}
library(knitr)
library(kableExtra)
library(drake)
library(ggplot2)
library(GGally)
stopifnot(
  requireNamespace("shiklomanov2017np", quietly = TRUE),
  requireNamespace("dplyr", quietly = TRUE),
  requireNamespace("tibble", quietly = TRUE)
)

@@

```{r echo = FALSE, results = "asis"}
prior_df <- tibble::tribble(
  ~param, ~mean, ~stdev,
  "Jmax_area", 2, 0.19,
  "Jmax_mass", 0, 0.26,
  "leaf_lifespan", 0.8, 0.4,
  "Narea", 0.25, 0.3,
  "Nmass", 1.25, 0.3,
  "Parea", -1, 0.3,
  "Pmass", 0, 0.3,
  "Rdarea", log10(0.0011), 0.15,
  "Rdmass", log10(0.8), 0.20,
  "SLA", 1, 0.6,
  "Vcmax_mass", log10(0.45), 0.2,
  "Vcmax_area", log10(50), 0.18
) %>%
  dplyr::mutate(variance = stdev ^ 2)

prior_df %>%
  dplyr::mutate(param = factor(param, shiklomanov2017np::both_params)) %>%
  dplyr::arrange(param) %>%
  dplyr::select(Trait = param, "Lognormal Mean" = mean, "Lognormal SD" = stdev) %>%
  knitr::kable(
    format = "latex",
    booktabs = TRUE,
    caption = paste(
      "Parameters for trait-specific prior distributions.",
      "For the multivariate and hierarchical distributions,",
      "the variance-covariance matrix prior was a diagonal matrix containing the",
      "square of the lognormal standard deviation values (i.e. the variance)",
      "shown here and all off-diagnoal terms set to zero." 
    )
  ) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))
```
